### 2023-12-14 sections/4-results.tex
trying to deal with merge conflict

@@

In Figure~\ref{fig:results:fashion-mnist-scaling}, which shows results for fashion-mnist, we observe that as the augmentation multiplier increases, the CAKES algorithms (GreedySieve in blue, RepeatedRnn in green, and Sieve in red) exhibit higher throughput than na\"{i}ve linear search, plotted in orange. We also observe that CAKES outperforms state-of-the-art similarity search algorithm FAISS-Flat (plotted in brown) for all cardinality multipliers and outperforms FAISS-IVF (plotted in pink) for all multipliers greater than $10^{5.5}$. Though state-of-the-art algorithms HNSW (plotted in gray), and Annoy (plotted in purple) have higher throughput than CAKES for all multipliers, we note that CAKES exhibits perfect recall for all multipliers, while hnsw and annoy exhibit much lower recall, as shown in Table~\ref{table:results:ann-fashion}. For example, at a cardinality multiplier as low as eight, hnsw and annoy have recall of 0.525 and 0.857 respectively, while CAKES exhibits perfect recall.
Amongst the CAKES algorithms, GreedySieve consistently performs best on this dataset, exhibiting sublinear time performance for nearly all cardinality multipliers.

With glove-25 (Figure~\ref{fig:results:glove-25-scaling}), we observe that each of CAKES' algorithms outperforms linear search at high cardinality multipliers. Similar to the results for fashion-mnist, we observe that CAKES outperforms FAISS-Flat for all cardinality multipliers and outperforms FAISS-IVF for all multipliers greater than $10^{7}$. We also see that while hnsw and annoy have higher throughput than CAKES for all multipliers, CAKES exhibits perfect recall for all multipliers, while hnsw and annoy exhibit much lower recall, as shown in Table~\ref{table:results:ann-glove-25}. For example, at a cardinality multiplier as low as eight, hnsw and annoy have recall of 0.294 and 0.857 respectively, while CAKES exhibits perfect recall.
On this dataset, Repeated $\rho$-NN, plotted in green, is consistently the best-performing algorithm. {\color{red} Revive lfd violin plots to add explanation for this.}

>>>>

Tables \ref{table:results:ann-fashion}, \ref{table:results:ann-glove-25}, \ref{table:results:ann-sift}, and \ref{table:results:ann-random} show the throughput and recall of CAKES's algorithms at each cardinality multiplier (i.e., scale) for the fashion-mnist, glove-25, sift, and random datasets respectively. When reporting recall, we use 1.000* to denote that the recall is imperfect, but rounds to 1.000 when we consider
only three decimal places.
Figures~\ref{fig:plots:fashion-mnist-scaling}A, ~\ref{fig:plots:glove-25-scaling}B, and ~\ref{fig:plots:sift-scaling}C show the scaling behavior of CAKES on augmented versions of the following ann-benchmark datasets: fashion-mnist under Euclidean distance, glove-25 under cosine distance, and sift under Euclidean distance. 
Figure~\ref{fig:plots:random-scaling}D shows the scaling behavior of CAKES on a completely randomly generated dataset with same cardinality and dimensionality as sift (1 million points in 128 dimensions).
The horizontal axis in each figure denotes the multiplier by which we increased the cardinality of the original dataset with synthetic points (see Section \ref{subsec:methods:synthetic-data}). 
The vertical axis denotes throughput in queries per second. Both axes are on a logarithmic scale. In this section, we discuss results only for $k$-NN search with $k = 10$, but similar plots for $k=100$ can be found in our Supplement section. In these plots, we label the recall at each scale for algorithms which do not exhibit perfect recall; if no such labels are given for an algorithm, then that algorithm exhibits perfect recall at all scales.

@@

In Figure~\ref{fig:results:fashion-mnist-scaling}, which shows results for fashion-mnist, we observe that as the augmentation multiplier increases, the CAKES algorithms (GreedySieve in blue, RepeatedRnn in green, and Sieve in red) exhibit higher throughput than na\"{i}ve linear search, plotted in orange. We also observe that CAKES outperforms state-of-the-art similarity search algorithm FAISS-Flat (plotted in brown) for all cardinality multipliers and outperforms FAISS-IVF (plotted in pink) for all multipliers greater than $10^{5.5}$. Though state-of-the-art algorithms HNSW (plotted in gray), and Annoy (plotted in purple) have higher throughput than CAKES for all multipliers, we note that CAKES exhibits perfect recall for all multipliers, while hnsw and annoy exhibit much lower recall, as shown in Table~\ref{table:results:ann-fashion}. For example, at a cardinality multiplier as low as eight, hnsw and annoy have recall of 0.525 and 0.857 respectively, while CAKES exhibits perfect recall.
Amongst the CAKES algorithms, GreedySieve consistently performs best on this dataset, exhibiting sublinear time performance for nearly all cardinality multipliers. 
In Figure~\ref{fig:results:fashion-mnist-scaling}, which shows results for fashion-mnist, we observe that as the augmentation multiplier increases, the CAKES algorithms (GreedySieve in blue, RepeatedRnn in green, and Sieve in red) exhibit higher throughput than na\"{i}ve linear search, plotted in orange. We also observe that CAKES outperforms state-of-the-art similarity search algorithm FAISS-Flat (plotted in brown) for all cardinality multipliers and outperforms FAISS-IVF (plotted in pink) for all multipliers greater than $10^{5.5}$. Though state-of-the-art algorithms HNSW (plotted in gray), and Annoy (plotted in purple) have higher throughput than CAKES for all multipliers, we note that CAKES exhibits perfect recall for all multipliers, while hnsw and annoy exhibit much lower recall, as shown in Table~\ref{table:results:ann-fashion}. For example, at a cardinality multiplier as low as eight, hnsw and annoy have recall of 0.525 and 0.857 respectively, while CAKES exhibits perfect recall.
Amongst the CAKES algorithms, GreedySieve consistently performs best on this dataset, exhibiting sublinear time performance for nearly all cardinality multipliers.

With glove-25 (Figure~\ref{fig:results:glove-25-scaling}), we observe that each of CAKES' algorithms outperforms linear search at high cardinality multipliers. Similar to the results for fashion-mnist, we see that CAKES outperforms FAISS-Flat for all cardinality multipliers and outperforms FAISS-IVF for all multipliers greater than $10^{7}$. We also see that while hnsw and annoy have higher throughput than CAKES for all multipliers, CAKES exhibits perfect recall for all multipliers, while hnsw and annoy exhibit much lower recall, as shown in Table~\ref{table:results:ann-glove-25}. For example, at a cardinality multiplier as low as eight, hnsw and annoy have recall of 0.294 and 0.857 respectively, while CAKES exhibits perfect recall.
On this dataset, Repeated $\rho$-NN, plotted in green, is consistently the best-performing algorithm. {\color{red} Revive lfd violin plots to add explanation for this.}
